% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}
%-----------------------------------------------------------
%\usepackage{fullpage}
\usepackage{hyperref}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{10pt} \Large \textbf{#1} \normalsize}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\large \textbf{#1} \normalsize & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-5pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Matthew Boler}  & 770-855-5529\\
\#501 Webster Road, Lot 315 & meb0054@auburn.edu \\
Auburn, AL 36832 & \url{https://mattboler.github.io/}\\
\end{tabular*}
\\

\rule{\textwidth}{0.4pt}

\resheading{Education}

\begin{itemize}

\item
	\ressubheading{Auburn University}{Auburn, AL}{Ph.D., Mechanical Engineering}{Anticipated May 2025}

\item
	\ressubheading{Auburn University}{Auburn, AL}{M.S., Mechanical Engineering}{August 2021}
	\begin{itemize}
		\resitem{Thesis: "Observability-Informed Measurement Validation for Visual-Inertial Navigation"}
		\resitem{Advisor: Dr. Scott Martin}
	\end{itemize}

\item
	\ressubheading{Auburn University}{Auburn, AL}{B.S. Mechanical Engineering, Computer Science Minor}{May 2019}

\end{itemize}

\resheading{Experience}
\begin{itemize}

\item
	\ressubheading{GPS and Vehicle Dynamics Laboratory}{Auburn, AL}{Graduate Research Assistant}{2019 - Current}\\
	\vspace{10pt}

	\large \textbf{Multispectral Visual Navigation} \normalsize
	\vspace{-5pt}
	\begin{itemize}
		\resitem{Developed a Multi-State Constraint Kalman Filter (MSCKF) with holonomic constraints and online extrinsic calibration for GPS-denied infrared+INS ground vehicle navigation.}
		\resitem{Designed a full-smoothing visual-inertial SLAM system using ISAM2 and a novel geometric validation module for robust feature initialization.}
		\resitem{Reduced sensitivity of visual SLAM systems to dynamic environments by adaptively segmenting static and dynamic image regions using YOLO and monitoring feature behavior.}
	\end{itemize}

	\large \textbf{Autonomous Tiger Racing} \normalsize
	\vspace{-5pt}
	\begin{itemize}
		\resitem{Developed a robust ground-removal algorithm for LIDAR obstacle detection to handle large bank angles using a smoothed height-variance map in ROS and PCL.}
		\resitem{Developed a combined offline graph SLAM and online particle filter localization subsystem using LIDAR, wheel odometry, and IMU.}
		\resitem{Developed a lighweight path planning node in ROS to generate minimum-jerk trajectories at 200Hz.}
	\end{itemize}

\item
	\ressubheading{Sandia National Laboratories}{Albuquerque, NM}{Intern - Navigation, Pointing, and Control}{2020}
	\begin{itemize}
		\item Designed experiments to determine performance characteristics of image registration methods for multispectral/hyperspectral imaging systems.
		\item Implemented modified Fourier-Mellin, SIFT, and other algorithms to improve registration performance between visual-spectrum and hyperspectral images.
	\end{itemize}

\end{itemize}

\resheading{Skills}

\begin{description}
\item[Languages:]
C++, Python, Matlab, Julia
\item[Software:]
Git, \LaTeX, Docker, Robot Operating System (ROS) 1 and 2
\item[Libraries:]
Numpy, SciPy, Pandas, OpenCV, PyTorch, Eigen, PCL, Open3D, GTSAM
\end{description}

\end{document}
